Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Clean up todos
Remove omitted results

\todo{ACM format for review? With line numbers etc.}

\todo{Make ORCID visible in ACM style: "Right now we do not typeset ORCIDs" (Source: ACM Style Docs)}

\todo{Include e-mails}

@@

\todo{Sum up all the steps needed for the submission}

@@

	\section{Ommited results}
	\begin{enumerate}
		 \item The lower bound of $\Omega(\ell)$ for the scenario with at most $(1/3-1/k)$-augmentation
		 \item Costly cascade example (it is easy to present $k^2$ and $k\cdot \sqrt{k}$ (with different approach), and then we can combine these to obtain $k^3$)
		 \item $k$-competitive algorithm for the ring communication pattern
		 \item $O(\ell)$-competitive algorithm for $k=4$ and $k=5$
  \end{enumerate}

>>>>

\todo{ACM format for review? Is there any specific format like this? With line numbers etc.}

\todo{Include e-mails? Or shall we skip it for now.}

@@

@@
